---
title: "R Notebook"
output: 
  html_document: 
    self_contained: true
    lib_dir: libs
    theme: spacelab
    highlight: tango
    toc: true
    toc_float: true
params:
  Year:
    label: "Year"
    value: 2009
    input: slider
    min: 2005
    max: 2020
    step: 1
    sep: ""
  region:
    label: "region:"
    # value: Latin America and Caribbean
    value: South Asia
    input: select
    choices: [Select All,South Asia, Central and Eastern Europe, Middle East and North Africa, Latin America and Caribbean, Commonwealth of Independent States, North America and ANZ, Western Europe, Sub-Saharan Africa, Southeast Asia, East Asia]
  GDP:
    label: "Log.GDP.per.capita"
    input: checkbox
    value: True
  Social:
    label: "Social.support"
    input: checkbox
    value: True
  Health:
    label: "Healthy.life.expectancy.at.birth"
    input: checkbox
    value: True
  Generosity: 
    label: "Generosity"
    input: checkbox
    value: False
  Corruption:
    label: "Perceptions.of.corruption"
    input: checkbox
    value: True


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

# Introduction

The project aims to create a reusable report with the same structure of the data. The report will include exploratory data analysis and basic modeling. The report will do the same analysis when the input data is changed. However, input data should be in the same structure as the initial input data.

A test data will be created from initial data and the reusability that is mentioned above will be tested with this data.

The following link is the dataset that is considered for this project: https://www.kaggle.com/ajaypalsinghlo/world-happiness-report-2021

The data includes 149 countries and their region. Also, it includes econometric values for each country.

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(caret)
library(corrplot)
library(ggplot2)
library(corrgram) 
library(dlookr)
library(corrplot)
library(car)
library(DT)
library(tidyverse)
library(ggrepel)
library(ggthemes)
```

# Data

## Description of the dataset
The World Happiness Report is a landmark survey of the state of global happiness . The report continues to gain global recognition as governments, organizations and civil society increasingly use happiness indicators to inform their policy-making decisions. Leading experts across fields – economics, psychology, survey analysis, national statistics, health, public policy and more – describe how measurements of well-being can be used effectively to assess the progress of nations. The reports review the state of happiness in the world today and show how the new science of happiness explains personal and national variations in happiness.

The happiness scores and rankings use data from the Gallup World Poll . The columns following the happiness score estimate the extent to which each of six factors – economic production, social support, life expectancy, freedom, absence of corruption, and generosity – contribute to making life evaluations higher in each country than they are in Dystopia, a hypothetical country that has values equal to the world’s lowest national averages for each of the six factors. They have no impact on the total score reported for each country, but they do explain why some countries rank higher than others.


```{r message=FALSE, warning=FALSE}
d1 <- read.csv("world-happiness-report.csv")
d2 <- read.csv("world-happiness-report-2021.csv")
d2 <- d2  %>% select(ï..Country.name,Regional.indicator)
d2 <- merge(d1,d2, by="ï..Country.name")
df <- d2
```

```{r}
df$Regional.indicator %>% factor() %>% table()
```


```{r}
datatable(df, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T))
```

```{r}
# sum(is.na(df))
```

```{r}
# df <- drop_na(df)
```

```{r}
# sum(is.na(df))
```

```{r}
library(stargazer)
```


# `r params$Year`
```{r}
# year <- params$Year
# year

```

# Region assignment from input to here

# `r params$region`
```{r}
region <- params$region
if (region == "Select All")
{
  region <- unique(d2$Regional.indicator)
}
region

```



# Parameters assignment from input to here

```{r}
ls <- c()

if (params$GDP)
{
  ls <- c(ls, "Log.GDP.per.capita")
}
if (params$Social)
{
  ls <- c(ls, "Social.support")
}
if (params$Health)
{
  ls <- c(ls, "Healthy.life.expectancy.at.birth") 
}
if (params$Generosity)
{
  ls <- c(ls, "Generosity") 
}  
if (params$Corruption)
{
  ls <- c(ls, "Perceptions.of.corruption")
}
ls

```




# `r params$region`

# `r params$GDP`




```{r}
# df %>% head()
```

```{r}
# unique(df$year) %>% length()
```

```{r}
# unique(df$ï..Country.name) %>% length()

```

```{r}
# df %>% summary()
```
```{r}
# describe(df)
```
```{r}
# xtable
```


```{r}
# kable(summary(df), results='asis')
```





## Missing Values

```{r}
for(i in 3:ncol(df %>% dplyr::select(-Regional.indicator))){
  df[is.na(df[,i]), i] <- mean(df[,i], na.rm = TRUE)
  
}
```



```{r}

plt_data <- df %>% filter(year == params$Year)

# get top 5
df_top <- plt_data %>% select(ï..Country.name, year, Life.Ladder) %>% slice_max(Life.Ladder, n=5)

# get bottom 5
df_bottom <- plt_data %>% select(ï..Country.name, year, Life.Ladder) %>% slice_min(Life.Ladder, n=5)


```

```{r}
ggplot(df_top, aes(y = reorder(ï..Country.name, Life.Ladder), x = Life.Ladder)) + 
  labs(title=paste("The World Happiness Report", params$Year), x="Score", y = "Country") +
   geom_bar(stat="identity", fill = "darkred") + theme_classic()
```

```{r}
ggplot(df_bottom, aes(y = reorder(ï..Country.name, -Life.Ladder), x = Life.Ladder)) + 
  labs(title=paste("The World Unhappiness Report", params$Year), x="Score", y = "Country") +
   geom_bar(stat="identity", fill = "darkred") + theme_classic()
```

```{r}
bind_rows(df_top,df_bottom)%>%
ggplot()+geom_point(aes(x= Life.Ladder, y = Life.Ladder))+
geom_text_repel(aes(x=Life.Ladder, y = Life.Ladder, label = ï..Country.name))+
labs(title = 'Comparison of Top and Bottom 5 Countries',
    subtitle = paste('Based on Life Ladder,', params$Year),
    x= 'Life Ladder Score',
    y = 'Life Ladder Score')+theme_stata()
```

```{r}
# Correlation Matrix
cor_data <- cor(df[,3:11],use = "pairwise.complete.obs")
cor_data %>% datatable()
```




```{r message=FALSE, warning=FALSE}
# Plotting Corelation Matrix
corrplot(cor_data, method = "pie")
```


```{r message=FALSE, warning=FALSE}
datatable(normality(df[,3:12]))
```

```{r message=FALSE, warning=FALSE}

rr_top <- plt_data %>% select(Regional.indicator, year, Life.Ladder) %>% group_by(Regional.indicator) %>% summarize(mean_size = mean(Life.Ladder, na.rm = TRUE)) %>% slice_max(mean_size, n=5)

rr_bottom <- plt_data %>% select(Regional.indicator, year, Life.Ladder) %>% group_by(Regional.indicator) %>% summarize(mean_size = mean(Life.Ladder, na.rm = TRUE)) %>% slice_min(mean_size, n=5)

```

```{r message=FALSE, warning=FALSE}
ggplot(rr_top, aes(y = reorder(Regional.indicator, mean_size), x = mean_size)) + 
  labs(title=paste("The World's Happiness Region", params$Year, "(Top 5)"), x="Average Score", y = "Region") +
   geom_bar(stat="identity", fill = "darkred")+ theme_classic()
```

```{r message=FALSE, warning=FALSE}
ggplot(rr_bottom, aes(y = reorder(Regional.indicator, -mean_size), x = mean_size)) + 
  labs(title=paste("The World's Unhappiness Region", params$Year, "(Bottom 5)"), x="Average Score", y = "Region") +
   geom_bar(stat="identity", fill = "darkred") + theme_classic()
```



```{r}
bind_rows(rr_top,rr_bottom)%>%
ggplot()+geom_point(aes(x= mean_size, y = mean_size))+
geom_text_repel(aes(x= mean_size, y = mean_size, label = Regional.indicator))+
labs(title = 'Comparison of Top and Bottom 5 Regions',
    subtitle = paste('Based on Life Ladder,', params$Year),
    x= 'Mean Life Ladder Score',
    y = 'Mean Life Ladder Score')+theme_stata()
```


# `r params$Year` for Data


```{r message=FALSE, warning=FALSE}

YearAndName <- c("year", "ï..Country.name", "Life.Ladder", "Regional.indicator", "Negative.affect", "Positive.affect")

SelectingVar <- c(YearAndName, ls)

FilteredData <-df %>% filter(Regional.indicator == region)
FilteredData <-FilteredData %>% select(SelectingVar)

```



# Model
```{r message=FALSE, warning=FALSE}
DataForML <- FilteredData %>% select(-year,-ï..Country.name, -Regional.indicator)

```

```{r}
datatable(DataForML, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T))
```




```{r message=FALSE, warning=FALSE}
DataForML_numeric_vars <- 
  sapply(DataForML, is.numeric) %>% 
  which() %>% 
  names()


DataForML_correlations <- 
  cor(DataForML[,DataForML_numeric_vars],
      use = "pairwise.complete.obs")
```

```{r message=FALSE, warning=FALSE}
corrplot(DataForML_correlations, 
         method = "pie")
```


```{r message=FALSE, warning=FALSE}
regressionMetrics <- function(real, predicted) {
  # Mean Squera Error
  MSE <- mean((real - predicted)^2)
  # Root Mean Square Error
  RMSE <- sqrt(MSE)
  # Mean Absolute Error
  MAE <- mean(abs(real - predicted))
  # Median Absolute Error
  MedAE <- median(abs(real - predicted))
  # Mean Logarithmic Absolute Error
  MSLE <- mean((log(1 + real) - log(1 + predicted))^2)
  # Total Sum of Squares
  TSS <- sum((real - mean(real))^2)
  # Explained Sum of Squares
  RSS <- sum((predicted - real)^2)
  # R2
  R2 <- 1 - RSS/TSS
  
  result <- data.frame(MSE, RMSE, MAE, MedAE, MSLE, R2)
  return(result)
}
```




```{r}
k <- (DataForML %>% colnames() %>% length())
k
```


```{r message=FALSE, warning=FALSE}

step.model <- train(Life.Ladder ~., data = DataForML,
                    method = "leapBackward",
                    tuneGrid = data.frame(nvmax = 1:k)
                    )
step.model
```




```{r}
plot(step.model)
```




```{r}

lmModel <- lm(Life.Ladder ~., data = DataForML)


stargazer(lmModel, type = "text", 
          style = "apsr",
          title = "Regression results", 
          header = FALSE,
          single.row = T)


```




```{r}
factors <- DataForML %>% select(-Life.Ladder) %>% colnames()
formula <- ""
for (j in factors)
{
  formula <- paste(formula, j, sep = "+")
}
formula <- paste("Life.Ladder ~ -Life.Ladder", formula)
```
Formula for Regression : `r formula`

```{r}
model <- lm(Life.Ladder~. , data = DataForML, k = 5)
plot(model)
vif(model)
```
